Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-07-21 nir_companions.tex
update binary intro

\section{Binary synthetic spectral recovery}
\label{subsec:companion_recovery}
Since the differential method is ineffective for our dataset due to the RV separation between observations, we explored a second approach to detect the presence of the faint companion spectra. This second approach compares the observed spectra to combinations of synthetic spectral models using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}. {The temperature of synthetic spectra fitted to the companion will provide some indication of the companions spectral type, but will not produce a direct mass constraint that was the original aim of this work.}

>>>>

\section{Binary synthetic spectral recovery}
\label{subsec:companion_recovery}
We explore detecting the presence of the faint companion spectra in combination with the host star by applying spectral fitting of a binary model. The observed spectra are fitted with a combination of two synthetic spectral models, using \(\chi^{2}\) methods which have been extensively used in the literature~\citep[e.g.][]{astudillo-defru_harps_2015, passegger_fundamental_2016, zechmeister_spectrum_2018,nemravova_xtauri_2016}. {The parameters of the synthetic spectra fitted to the companion should provide an indication of the properties of the companion.}
